%-------------------------
% Resume in Latex
% Author : CHAN YH
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[sfdefault]{roboto}
\usepackage{raleway}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\fontfamily{Raleway-TLF}\selectfont \huge \textbf{CHAN YI HENG}} \\ \vspace{1pt}
    % \rmfamily \textbf{\Huge \scshape Chan Yi Heng} \\ \vspace{1pt}
    \small {\faPhoneSquare} +65 8862 0913 $|$
    \href{mailto:x@x.com}{{\faEnvelope} \underline{c@chanyh.com}} $|$ 
    \href {https://chanyh.com}{{\faGlobeAsia} \underline{chanyh.com}} $|$
    \href{https://github.com/cyh-chan}{{\faGithub} \underline{cyh-chan}} $|$
    \href{https://www.linkedin.com/in/chanyiheng/}{{\faLinkedin} \underline{chanyiheng}} $|$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{Singapore, SG}
      {Master of Science in Statistics}{Aug 2026 -- Expected 2027}
    \resumeSubheading
      {Singapore University of Social Sciences}{Singapore, SG}
      {Bachelor of Science (Honours) in Mathematics}{Jan 2022 -- Dec 2025}
    \resumeSubheading
      {Singapore Polytechnic}{Singapore, SG}
      {Diploma in Banking \& Finance}{Apr 2016 -- Mar 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Teaching Assistant}{Jan 2026 -- Apr 2026}
{Singapore University of Social Sciences}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Facilitated technical tutorials in Statistical Analysis covering probability theory, asymptotic inference, and classical linear regression.}
    \resumeItem{Formulated structural review frameworks to ground undergraduate cohorts in deductive mathematical reasoning and problem-solving.}
    \resumeItem{Guided student execution of formal model diagnostics, emphasizing verification of Gauss-Markov assumptions and residual structures.}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Oct 2025 -- Present}
{Singapore University of Social Sciences, University Research Office}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Formulated statistical inference frameworks for experimental psychometric data to quantify treatment effects on latent creativity constructs.}
    \resumeItem{Developing stochastic models for financial time-series data to capture non-stationarity, temporal dependencies, and volatility dynamics.}
    \resumeItem{Applying survival analysis and classification techniques to clinical datasets to isolate features driving patient non-attendance.}
    \resumeItem{Engineered reproducible data pipelines for high-dimensional institutional datasets to ensure mathematical integrity for academic review.}
\resumeItemListEnd

\resumeSubheading
{Research Intern}{Nov 2024 -- Aug 2025}
{A*STAR, Advanced Remanufacturing and Technology Centre}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Architected deep learning models for multi-horizon time-series forecasting under non-stationary demand conditions.}
    \resumeItem{Implemented a SHAP-based Explainable AI (XAI) framework to quantify localized feature attributions and map non-linear interactions.}
    \resumeItem{Evaluated contemporary deep learning baselines, optimizing hyperparameter spaces to enhance empirical robustness and performance bounds.}
\resumeItemListEnd

\resumeSubheading
{Finance Operations Analyst}{Sep 2021 -- Dec 2021}
{Indeed}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Audited cross-border financial data systems to ensure high-fidelity data migration and compliance with international reporting frameworks.}
    \resumeItem{Optimized workflows within Salesforce environments by implementing data validation protocols to minimize transactional errors.}
\resumeItemListEnd

\resumeSubheading
{Finance Specialist}{Aug 2019 -- Dec 2021}
{Singapore Armed Forces}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Managed operational budgets and resource allocations under central government regulatory frameworks.}
    \resumeItem{Executed internal audits and risk assessments, applying structured methodologies to report compliance metrics to leadership.}
    \resumeItem{Administered large-scale operational budgets during COVID-19 deployments, maintaining accuracy under highly volatile conditions.}
\resumeItemListEnd

\resumeSubheading
{Wealth Management Intern}{Sep 2018 -- May 2019}
{DBS Bank}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Conducted quantitative operational analyses, leveraging process data to isolate system inefficiencies and formulate optimization strategies.}
    \resumeItem{Enforced compliance protocols through the systematic validation of Accredited Investor documentation and data control frameworks.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------Research & PROJECTS-----------
\section{Research}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Predictive Analytics \& Financial Time-Series Modeling} $|$ \emph{Dr. Fan Zengyan}}{Jun 2026 -- Present}
\resumeItemListStart
    \resumeItem{Investigating non-stationary asset dynamics and temporal volatility dependencies within high-frequency financial time-series datasets.}
    \resumeItem{Deriving stochastic predictive architectures to model underlying market mechanisms, bypassing the limitations of traditional stationary assumptions.}
    \resumeItem{Engineering data ingestion pipelines to process and structure multi-asset institutional streaming data from Bloomberg terminals for rigorous downstream quantitative estimation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Stratified Non-Attendance Modeling in Clinical Datasets} $|$ \emph{Dr. Fan Zengyan}}{Jun 2026 -- Present}
\resumeItemListStart
    \resumeItem{Establishing a quantitative framework to isolate the demographic and behavioral covariates driving stratified patient non-attendance in localized clinical settings.}
    \resumeItem{Formulating survival analysis and categorical data models to evaluate time-to-event dynamics and map high-variance predictors of non-compliance.}
    \resumeItem{Deriving statistical diagnostics to adjust for real-world irregularities, applying heteroscedasticity-consistent estimators and non-parametric variance partitioning.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Causal Machine Learning for Treatment Heterogeneity Modeling} $|$ \emph{Dr. Fan Zengyan}}{Oct 2025 -- Jun 2026}
\resumeItemListStart
    \resumeItem{Investigated conditional treatment heterogeneity across high-dimensional feature spaces to derive welfare-maximizing assignment rules.}
    \resumeItem{Architected a tripartite causal machine learning framework, benchmarking Meta-Learners against Causal Forest Double Machine Learning to isolate individualized treatment effect surfaces.}
    \resumeItem{Enforced a rigorous identification protocol utilizing cross-validated propensity scores and deterministic boundary trimming to satisfy overlap assumptions and bound regularization bias.}
    \resumeItem{Synthesized localized individualized treatment effect vectors into an unsupervised clustering matrix to extract latent responder archetypes, validating results via an Optimal Policy Tree algorithm.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Multivariate Time Series Forecasting for Equity Price Prediction} $|$ \emph{Dr. Zhou Tianyi}}{Jan 2025 -- Nov 2025}
\resumeItemListStart
    \resumeItem{Evaluated the out-of-sample empirical stability of multi-horizon (1-, 5-, 20-day) return forecasting frameworks across NYSE-listed equities under non-linear asset dynamics.}
    \resumeItem{Conducted systematic comparative evaluations of classical linear estimators against sequential deep learning and contemporary self-attention architectures.}
    \resumeItem{Isolated economically meaningful technical signals via ensemble-based XGBoost feature selection pipelines, utilizing Recursive Feature Elimination and permutation importance.}
    \resumeItem{Validated the predictive superiority of attention mechanisms in capturing long-range dependencies through rigorous walk-forward backtesting regimes.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Data-Driven Framework for Enhancing Supply Chain Resilience} $|$ \emph{Dr. Liu Ning}}{Nov 2024 -- Aug 2025}
\resumeItemListStart
    \resumeItem{Investigated the theoretical and empirical performance boundaries of deep learning optimization architectures for stochastic inventory control against classical Predict-Then-Optimize paradigms.}
    \resumeItem{Synthesized dilated temporal Convolutional Neural Networks and Multi-Quantile Recurrent Neural Networks to model probabilistic, non-stationary demand distributions.}
    \resumeItem{Captured long-range temporal dependencies to optimize direct cost-functions in high-variance multi-SKU simulation environments.}
    \resumeItem{Demonstrated significant structural cost reductions and enhanced system resilience relative to traditional heuristic benchmarks.}
\resumeItemListEnd

\resumeSubHeadingListEnd

      % {\textbf{Personal Website} $|$ \emph{HTML/CSS, JavaScript}}{May 2024 -- Jun 2024}
      % \resumeItemListStart
      %   \resumeItem{Designed and developed a personal website using HTML, CSS, and JavaScript, showcasing strong front-end development skills}
      %   \resumeItem{Deployed the website to a GitHub repository, demonstrating proficiency in version control and collaborative coding practices}
      %   \resumeItem{Hosted the website under a personal domain using Cloudflare, ensuring reliable and secure access with optimized performance}
      %   \resumeItem{Implemented responsive design principles to ensure the website is user-friendly across various devices and screen sizes}
      %   \resumeItem{Utilized Cloudflare services for enhanced security, performance optimization, and efficient content delivery, improving user experience and site reliability}
      % \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{COVID-19 Safe-Entry Clone System} $|$ \emph{HTML/CSS, JavaScript, SQL}}{Sep 2020}
      %     \resumeItemListStart
      %       \resumeItem{Developed a Safe Entry clone system to log visitor entries at various locations during the COVID-19 pandemic, facilitating effective contact tracing}
      %       \resumeItem{Utilized front-end technologies like HTML, CSS, and JavaScript to create a user-friendly interface for seamless visitor check-in}
      %       \resumeItem{Integrated a MySQL database to store visitor logs securely and ensure quick retrieval for health authorities}
      %       \resumeItem{Designed the system to comply with data privacy regulations, ensuring sensitive information is handled responsibly}
      %       \resumeItem{Enhanced the system with real-time reporting features to assist health authorities in tracking and isolating potential COVID-19 clusters efficiently}
      %     \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Digitalization by Frank, OCBC} $|$ \emph{Microsoft Suite, Adobe XD}}{Apr 2018 -- Jun 2018}
      %     \resumeItemListStart
      %       \resumeItem{Collaborated with a team of four to propose and prototype innovative digitalization strategies aimed at enhancing OCBC Bank's appeal to younger customers}
      %       \resumeItem{Conducted market research to identify the digital banking needs and preferences of the youth demographic, informing the development of targeted solutions}
      %       \resumeItem{Designed user-friendly mobile app features and an intuitive interface to improve user engagement and streamline banking experiences for young customers}
      %       \resumeItem{Developed interactive prototypes using Adobe XD, demonstrating proposed features and enhancements to OCBC stakeholders}
      %       \resumeItem{Presented project findings and prototypes to OCBC executives, providing actionable insights and recommendations for future digital banking initiatives}
      %       \resumeItem{Received positive feedback from OCBC stakeholders, highlighting the potential impact of the proposed digitalization strategies on customer satisfaction and retention}
      %     \resumeItemListEnd


%
%-----------Competency-----------
\section{Competency}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Scripting}{: Python, R, SQL, LaTeX} \\
     \textbf{Development \& Tools}{: Git, VS Code, Visual Studio, Jupyter} \\
     \textbf{Spoken Languages}{: English (Fluent), Mandarin (Native)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
